CA of Music Genre Stereotypes

### 2025-05-09 analysis-bb.qmd
new stuff

   # Class
   png(file = here("Plots", "demog-lower-subjclass.png"), width=w, height=h)
   make.demog.plot(make.demog.dat(row.lab.dat.id, "Lower_Class", "subjclass"), 
                    "Lower_Class", "subjclass", r = 3)   
   dev.off()
   png(file = here("Plots", "demog-working-subjclass.png"), width=w, height=h)
   make.demog.plot(make.demog.dat(row.lab.dat.id, "Working_Class", "subjclass"), 
                    "Working_Class", "subjclass", r = 3)   
   dev.off()
   png(file = here("Plots", "demog-middle-subjclass.png"), width=w, height=h)
   make.demog.plot(make.demog.dat(row.lab.dat.id, "Middle_Class", "subjclass"), 
                    "Middle_Class", "subjclass", r = 3)   
   dev.off()
   png(file = here("Plots", "demog-upper-subjclass.png"), width=w, height=h)
   make.demog.plot(make.demog.dat(row.lab.dat.id, "Upper_Class", "subjclass"), 
                    "Upper_Class", "subjclass", r = 3)   
   dev.off()
```

```{r Demographic Specific Cloud Variance Plots}
   h <- 700
   w <- 700
   make.demog.var.dat <- function(w, g, d) {
      a <- make.demog.dat(w, g, d) 
      b <- a %>% 
         group_by_at(8) %>% 
         summarize(across(1:3, mean)) %>% 
         rename(Prot.1 = Dim.1, Prot.2 = Dim.2, Prot.3 = Dim.3) %>% 
         right_join(a) %>% 
         mutate(dist.cent.1 = (Dim.1 - Prot.1)^2) %>% 
         mutate(dist.cent.2 = (Dim.2 - Prot.2)^2) %>% 
         mutate(dist.cent.3 = (Dim.3 - Prot.3)^2) %>% 
         mutate(var = dist.cent.1 + dist.cent.2 + dist.cent.3) %>% 
         group_by_at(1) %>% 
         summarize(var = mean(var)) %>% 
         rename(col.obj = 1)
      return(b)
   }
   # Education
   png(file = here("Plots", "demog-classical-educ-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Classical", "educ.f"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-jazz-educ-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id,
                                          "Jazz", "educ.f"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-opera-educ-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Opera", "educ.f"), ps = 12) 
   dev.off()
   # Race
   png(file = here("Plots", "demog-jazz-race-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Jazz", "race"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-rap-race-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Rap", "race"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-folk-race-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Folk", "race"), ps = 12) 
   dev.off()
   # Age
   png(file = here("Plots", "demog-metal-age-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Metal", "age"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-rap-age-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Rap", "age"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-altrock-age-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Alt_Rock", "age"), ps = 12) 
   dev.off()
   # Class
   png(file = here("Plots", "demog-lower-subjclass-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
                                          "Lower_Class", "subjclass"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-working-subjclass-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
                                          "Working_Class", "subjclass"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-middle-subjclass-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
                                          "Middle_Class", "subjclass"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-upper-subjclass-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
                                          "Upper_Class", "subjclass"), ps = 12) 
   dev.off()
```

>>>>

   # Class
   png(file = here("Plots", "demog-lower-subjclass.png"), width=w, height=h)
   make.demog.plot(make.demog.dat(row.lab.dat.id, "Lower_Class", "subjclass"), 
                    "Lower_Class", "subjclass", r = 3)   
   dev.off()
   png(file = here("Plots", "demog-working-subjclass.png"), width=w, height=h)
   make.demog.plot(make.demog.dat(row.lab.dat.id, "Working_Class", "subjclass"), 
                    "Working_Class", "subjclass", r = 3)   
   dev.off()
   png(file = here("Plots", "demog-middle-subjclass.png"), width=w, height=h)
   make.demog.plot(make.demog.dat(row.lab.dat.id, "Middle_Class", "subjclass"), 
                    "Middle_Class", "subjclass", r = 3)   
   dev.off()
   png(file = here("Plots", "demog-upper-subjclass.png"), width=w, height=h)
   make.demog.plot(make.demog.dat(row.lab.dat.id, "Upper_Class", "subjclass"), 
                    "Upper_Class", "subjclass", r = 3)   
   dev.off()

   # Education
   png(file = here("Plots", "demog-college-educ.png"), width=w, height=h)
   make.demog.plot(make.demog.dat(row.lab.dat.id, "College", "educ.f"), 
                    "College", "educ.f", r = 3)   
   dev.off()
   png(file = here("Plots", "demog-nocollege-educ.png"), width=w, height=h)
   make.demog.plot(make.demog.dat(row.lab.dat.id, "No_College", "educ.f"), 
                    "No_College", "educ.f", r = 3)   
   dev.off()
```

```{r Demographic Specific Cloud Variance Plots}
   h <- 700
   w <- 700
   make.demog.var.dat <- function(w, g, d) {
      a <- make.demog.dat(w, g, d) 
      b <- a %>% 
         group_by_at(8) %>% 
         summarize(across(1:3, mean)) %>% 
         rename(Prot.1 = Dim.1, Prot.2 = Dim.2, Prot.3 = Dim.3) %>% 
         right_join(a) %>% 
         mutate(dist.cent.1 = (Dim.1 - Prot.1)^2) %>% 
         mutate(dist.cent.2 = (Dim.2 - Prot.2)^2) %>% 
         mutate(dist.cent.3 = (Dim.3 - Prot.3)^2) %>% 
         mutate(var = dist.cent.1 + dist.cent.2 + dist.cent.3) %>% 
         group_by_at(1) %>% 
         summarize(var = mean(var)) %>% 
         rename(col.obj = 1)
      return(b)
   }
   # Education
   png(file = here("Plots", "demog-classical-educ-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Classical", "educ.f"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-jazz-educ-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id,
                                          "Jazz", "educ.f"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-opera-educ-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Opera", "educ.f"), ps = 12) 
   dev.off()
   # Race
   png(file = here("Plots", "demog-jazz-race-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Jazz", "race"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-rap-race-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Rap", "race"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-folk-race-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Folk", "race"), ps = 12) 
   dev.off()
   # Age
   png(file = here("Plots", "demog-metal-age-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Metal", "age"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-rap-age-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Rap", "age"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-altrock-age-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.gen.dat.id, 
                                          "Alt_Rock", "age"), ps = 12) 
   dev.off()
   # Class
   png(file = here("Plots", "demog-lower-subjclass-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
                                          "Lower_Class", "subjclass"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-working-subjclass-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
                                          "Working_Class", "subjclass"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-middle-subjclass-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
                                          "Middle_Class", "subjclass"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-upper-subjclass-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
                                          "Upper_Class", "subjclass"), ps = 12) 
   dev.off()

   # Education
   png(file = here("Plots", "demog-college-educ-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
                                          "College", "educ.f"), ps = 12) 
   dev.off()
   png(file = here("Plots", "demog-nocollege-educ-var.png"), width=w, height=h)
   make.var.plot.demog(make.demog.var.dat(row.lab.dat.id, 
                                          "No_College", "educ.f"), ps = 12) 
   dev.off()
```
